Capstone Movielens Report

### 2025-12-25 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Report sections review: the model tuning & regularization.

::: {.noteblock data-latex=""}
Since the `degree` parameter can only take three discrete values, 0, 1, and 2, we will perform the tuning in three steps - one for each possible value of the `degree`.
:::

@@

#### UMGYDE Model Tuning: Step 1 (`degree = 0`)
\

@@

#### UMGYDE Model Tuning: Step 2 (`degree = 1`)
\

@@

#### UMGYDE Model Tuning: Step 3 (`degree = 2`)
\

>>>>

@@

::: {.noteblock data-latex=""}
The complete source code of the solution described in this section is available in the [UMGYDE Model Tuning by `span` & `degree` parameters](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1553) section of the [capstone-movielens.main.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L1553) script on _GitHub_.
:::

Since the `degree` parameter can only take three discrete values, 0, 1, and 2, we will perform the tuning in three stages - one for each possible value of the `degree`.

For each value of the `degree` parameter, we will divide each stage into the following two steps for tuning the model by the `span` parameter:

  1. **Pre-configuration:**  Preliminary determination of the optimal range of the `span` parameter values for the *K-Fold Cross-Validation* samples, where the $K$ is the length of the [`edx_CV` Object] (described in detail in [Appendix B: Models Training Datasets]) to which the *K-Fold Cross-Validation* is applied (in *this Project* we use $K = 5$);

  2. **Fine-tuning:** Determining the best value of the `span` parameter with the highest possible accuracy that minimizes the *RMSE* score for the model.

Finally, we will retrain the model with the best `degree` and `span` values determined by the tuning result.

#### UMGYDE Model Tuning: Stage 1 (`degree = 0`)
\

@@

#### UMGYDE Model Tuning: Stage 2 (`degree = 1`)
\

@@

#### UMGYDE Model Tuning: Stage 3 (`degree = 2`)
\
